---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 8, fig.height = 8,
  out.width = "100%"
)
```

# hexwords

<!-- badges: start -->
<!-- badges: end -->

The goal of hexwords is to find words that are colours. 

## Installation

You can install the dev version of hexwords from github  with:

``` r
remotes::install_github("mdsumner/hexwords")
```

## Example

This is a basic example which shows you the colour of several english words, it's extremely interesting and important. 

```{r example}
library(hexwords)
## basic example code
op <- par(mar = rep(0, 4), bg = "darkgrey")
plot(seq_along(english_hex), col = sprintf("#%s", english_hex), pch = 19, cex = 5, asp = 1, ylim = c(-0.2, length(english_hex) + 0.2), xlim = c(0, length(english_hex)  + 1), xlab = "", ylab = "", axes = F)
text(seq_along(english_hex), lab = english_hex, srt = 15, cex = 0.9, pos = 4, offset = 1)
par(op)
```

## Code of Conduct
  
Please note that the hexwords project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
